LSTM for Sentiment Analysis on Twitter

### 2015-12-20 paper/paper.tex
fill in some corpus stats

\section{Experiments}

\subsection{Datasets}

\subsection{Results}

\begin{table}[h!]
\centering
\caption{Accuracy across LSTMs}
\label{char-models}
\begin{tabular}{|l|ll|}
\hline
              & 1.6M           & semeval \\
\hline
ascii/rnd/50  & \textbf{83.84} & 82.08   \\
ascii/rnd/200 & 82.45          & 83.53   \\
ascii/eye/50  & 77.44          &         \\
utf8          & 81.34          & 82.34   \\
word/rnd      & 81.85          & 78.07   \\
word/sswe     & 83.24          & 79.27   \\
\hline
\end{tabular}
\end{table}

>>>>

\section{Results}

\subsection{Datasets}
We conduct our experiments on two datasets: the latest benchmark dataset for SemEval 2016 and the dataset provided by \cite{go2009twitter}. In the latter dataset, the training set consists of $1.6$ million weakly-supervised tweets collected during $2009$, and the test set is hand-labeled. In the experiments presented below, we first train our models on the Go dataset, then re-train the model parameters on the smaller, fully-supervised SemEval dataset.

\begin{table}[h!]
\centering
\caption{Data size and label distribution}
\label{my-label}
\begin{tabular}{|lllll|}
\hline
      & \multicolumn{2}{l}{Go et. al. (1.6M)} & \multicolumn{2}{l}{SemEval2016} \\
      & neg               & pos               & neg            & pos            \\
\hline
train & 800000            & 800000            & 781            & 2805           \\
dev   & -                 & -                 & 358            & 766            \\
test  & 177               & 182               & 286            & 886           \\
\hline
\end{tabular}
\end{table}

\subsection{Experiments}
We compare the performance of character-level models against word-level models. For the former, we compare across character sets (``utf8'' and ``ascii''), parameter initializations (``rnd'' and ``eye''), and embedding dimension sizes ($50$ and $200$). The vocabulary for the ``utf8'' setting consisted of $1949$ characters, and for ``ascii'' consisted of $93$ characters. We initialize model parameters randomly at all levels in the ``rnd'' setting whereas in the ``eye'' setting, we initialize the second-level LSTM cell and gate parameters using the identity matrix.

For the latter, we compare initializing the word embeddings using random vectors (``word/rnd'') against initialization using the embeddings provided in \cite{tang2014learning} (``word/sswe'').

\begin{table}[h!]
\centering
\caption{Accuracy across LSTMs}
\label{char-models}
\begin{tabular}{|l|ll|}
\hline
              & 1.6M (acc)          & semeval (acc) \\
\hline
ascii/rnd/50  & \textbf{83.84} & 82.08   \\
ascii/rnd/200 & 82.45          & \textbf{84.13}   \\
ascii/eye/50  & 77.44          & 79.18   \\
utf8          & 81.34          & 82.34   \\
word/rnd      & 81.85          & 78.07   \\
word/sswe     & 83.24          & 79.27   \\
\hline
\end{tabular}
\end{table}

\subsection{Analysis}
